Choosing an appropriate scalar transformation to normalise wpd

### 2021-02-04 scalar_transformation.Rmd
figure caption update
date removed

---
title: "Choosing an appropriate scalar transformation to normalise wpd"
author: "Sayani Gupta"
date: "28/01/2021"
output: pdf_document
---

@@

```{r raw, fig.cap="Distribution of raw wpd is plotted across different nx and nfacet categories. Both shape and scale of the distribution changes for different nx and nfacet categories."}
N01 %>% 
  ggplot(aes(x = value)) + 
  geom_density(fill = "blue") +
  facet_grid(nx~nfacet,
             labeller = "label_both") + 
  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
  xlab("raw wpd")
```

>>>>

---
title: "Choosing an appropriate scalar transformation to normalise wpd"
author: "Sayani Gupta"
output: pdf_document
---

@@

```{r raw, fig.cap = "Distribution of raw wpd is plotted across different nx and nfacet categories. Both shape and scale of the distribution changes for different nx and nfacet categories."}
N01 %>% 
  ggplot(aes(x = value)) + 
  geom_density(fill = "blue") +
  facet_grid(nx~nfacet,
             labeller = "label_both") + 
  scale_x_continuous(breaks = scales::breaks_extended(3)) + 
  xlab("raw wpd")
```
